Language-Based Security for Low-Level MPC

### 2024-08-30 ppdp24/slides.tex
checkpoint

>>>>

\section{What's an MPC Protocol}
\begin{frame}

  A \cemph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$, where
  the inputs are the secrets of clients.

  Low-level, probabilistic protocols are defined in terms of basic variable types:
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\reveal{x}$: broadcast messages.
  \item $\flip{x}$: a uniformly random sample from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \item $\pubout$: a protocol output
  \end{itemize}
  We can localize variables and expressions to \emph{clients}, and any information
  exchanged between clients must be through messaging.
  \begin{block}{Example}
    $$
    \mx{x}{1} := \elab{(\secret{x} - \flip{x})}{2}
    $$
  \end{block}
\end{frame}
